AdaptiveConformal: An `R` Package for Adaptive Conformal Inference

### 2024-06-13 paper.qmd
Fixed typo, updated lock file

Overall, our findings illustrate strengths and weaknesses of all the considered algorithms. The original ACI algorithm is appealing in its simplicity, although its performance depends entirely on a good choice of its tuning parameter. AgACI tended to perform well in the simulation studies in terms of coverage error, although it had slightly higher strongly adaptive regret than other algorithms in some settings. However, there are relatively fewer theoretical guarantees available for AgACI than the other methods. DtACI, SF-OGD, and SAOCP all feature strong theoretical results, although they exhibited some differences in the simulation studies, with SF-OGD and SAOCP slightly undercovering in some scenarios. SAOCP also had longer path lengths than other methods in simulations, although in practice in the influenza forecasting task longer path lengths does not seem to effect the plausability of the prediction intervals the algorithm produces.

>>>>

Overall, our findings illustrate strengths and weaknesses of all the considered algorithms. The original ACI algorithm is appealing in its simplicity, although its performance depends entirely on a good choice of its tuning parameter. AgACI tended to perform well in the simulation studies in terms of coverage error, although it had slightly higher strongly adaptive regret than other algorithms in some settings. However, there are relatively fewer theoretical guarantees available for AgACI than the other methods. DtACI, SF-OGD, and SAOCP all feature strong theoretical results, although they exhibited some differences in the simulation studies, with SF-OGD and SAOCP slightly undercovering in some scenarios. SAOCP also had longer path lengths than other methods in simulations, although in practice in the influenza forecasting task longer path lengths does not seem to effect the plausibility of the prediction intervals the algorithm produces.
